Network Configuration Synthesis with Abstract Topologies

### 2016-11-12 paper/abstraction/paper.tex
update images
edits to 4

Second, \sysname checks if the fault-tolerance policy can be met by considering the joint impact of the abstract topology and routing policy. Joint analysis is needed, because connectivity for traffic will suffer even when functional paths exists in the topology if those paths are not allowed by routing policy. It implies that we cannot use standard graph theoretic algorithms.

Instead, we develop a sound analysis based on computing the minimum number of disjoint policy-compliant paths between pairs of nodes over abstract topologies. If this number for a pair of nodes is less than the desired fault-tolerance level, \sysname declares that the policy cannot be met.

Suppose we want to compute the number of of disjoint paths between any global ToR and spine router in Figure~\ref{fig:example3} for any concrete topology after applying the routing policy.
%This can be used as a lightweight verification tool to detect certain classes of configuration bugs. For example, since the network is performing prefix summarization at the border of the datacenter, we might introduce a black hole after enough failures occur to disconnect a tor from a spine router.
For each abstract role in the network, we learn invariants about the number of disjoint paths to routers in that role. These invariants contain a sequence of labels followed by a pair of numbers $(i,j)$. For example, the analysis would start with a fact of the form: $S_P S_{TG} (1,1)$. This means that, there is some group of nodes of size 1 in the TG role in some pod P such that any initial node in the TG role has 1 disjoint path to it (and all such paths are edge-disjoint). Since we know that the each node in the TG role is in a full mesh with nodes in the AG role within any given pod, we might infer a fact for AG of the form: $S_P A_{AG}(e1,1)$. This says that any group of nodes of size e1 in the AG role is reachable with at least 1 edge-disjoint path to each such node from any initial node in the TG role.
%
After one more inference the analysis will learn a fact of the form $A_{S}(1,1)$, which means that any single spine node is reachable via a single disjoint path from any initial global ToR node 
In fact, due the the valley-free routing constraint, a single path is the most information we can infer, since this is exactly the worst-case fault-tolerance for the concrete network from Figure~\ref{fig:example2}.

@@

\begin{figure}[t!]
  \begin{code}
    \Template{S}
      Match[100] \PREFIX=\$GP, \PEER=\{AG, AL\}
        \PEER \Arrow *
      Match[100] \PREFIX=\$LP, \PEER=\{AG, AL\}
        \PEER \Arrow \{AG, AL\}
      Match[110] \PREFIX=true \PEER=\{P1\},
        \PEER \Arrow *, \COMM \Arrow (1,0)
      Match[100] \PREFIX=true \PEER=\{P2\},
        \PEER \Arrow *, \COMM \Arrow (0,1)
      ...
  \end{code}

  \vspace{-2em}
  \begin{code}
    \Router{S1, S2}
      Match[100] \PREFIX=GP1, \PEER=\{AG1, AL1, ...\}
        \PEER \Arrow *
      Match[100] \PREFIX=GP2, \PEER=\{AG1, AL1, ...\}
        \PEER \Arrow *
      ...
      Match[100] \PREFIX=LP1, \PEER=\{AG1, AL1, ...\}
        \PEER \Arrow \{AG1, AL1, ...\}
      Match[100] \PREFIX=LP2, \PEER=\{AG1, AL1, ...\}
        \PEER \Arrow \{AG1, AL1, ...\}
      ...
      Match[110] \PREFIX=true, \PEER=\{P1\},
        \PEER \Arrow *, \COMM \Arrow (1,0)
      Match[100] \PREFIX=true, \PEER=\{P2\},
        \PEER \Arrow *, \COMM \Arrow (0,1)
      ...
    \end{code}

  \vspace{-1em}
  \caption{Spine template and concrete configurations.}
  \label{fig:bgp-configs}
\end{figure}

>>>>

Second, \sysname checks if the fault-tolerance policy can be met by considering the joint impact of the abstract topology and routing policy. Joint analysis is needed, because connectivity depends on both: traffic will not flow along
valid topological paths if the routing policy disallows it. 
\dpw{I deleted this:  ``It implies that we cannot use standard graph theoretic algorithms.''  I don't know of any ``standard'' graph-theoretic algorithm
we could use but I can't completely rule it out either because I don't
know all graph theoretic algorithms and it wouldn't completely shock 
me if somewhere there were algorithms for analyzing graphs modulo
isomorphisms that might be related tangentially.  Basically, I think
it brings up the possibility that we should compare with graph-theoretic
algorithms but then we don't do so in any detail
so I thought it was better to drop it.}

Instead, we develop a sound analysis based on computing the minimum
number of edge-disjoint policy-compliant paths between pairs of nodes
over abstract topologies. If this number for a pair of nodes is less
than the desired fault-tolerance level, \sysname declares that the
policy cannot be met.  More specifically,
for each abstract role in the network, our analysis will learn facts about the
number of disjoint paths to routers in that role.  For example,
the fact $A_{S}(2,3)$ states that for \emph{all} groups of 2 nodes
in the $S$ (Spine) role, there are 6 disjoint paths to the group---3 
for each of the 2 nodes. A fact such as $S_{S}(2,3)$, states that
\emph{some} group of 2 nodes has the property as opposed to all.
More generally, there is one quantifier ($A$ for all groups
and $S$ for exists a group).  When nodes are nested within pods,
there is one quantifier for each level of the hierarchy, so
$S_P S_{TG} (i,j)$ means that for some pod from the $P$ group of pods
and for some nodes in the $TG$ role within that pod, there exists a
group of $i$ nodes with $j$ paths to each node in the group.

As an example, suppose we want to compute the number of of disjoint paths 
between any
global ToR and spine router in Figure~\ref{fig:example3}.
%This can be used as a lightweight verification tool to detect certain classes of configuration bugs. For example, since the network is performing prefix summarization at the border of the datacenter, we might introduce a black hole after enough failures occur to disconnect a tor from a spine router.
The analysis begins with the fact
$S_P S_{TG} (1,1)$---there is some group of
nodes of size 1 in the $TG$ role in some pod $P$ such that any initial
node in the $TG$ role has 1 disjoint path to it (and all such paths are
edge-disjoint). Since the abstract topology specifies that each node in 
the $TG$ role is in
a full mesh with nodes in the $AG$ role within any given pod, we 
infer the fact $S_P A_{AG}(e1,1)$. This says that
any group of nodes of size e1 in the $AG$ role is reachable with at
least 1 path to each such node from any initial node in
the $TG$ role.
%
After one more step, the analysis will learn a fact of the form $A_{S}(1,1)$, which means that any single spine node is reachable via a single disjoint path from any initial global ToR node 
In fact, due the the valley-free routing constraint, a single path is 
the worst-case fault-tolerance level for the concrete network from 
Figure~\ref{fig:example2}.

@@

\begin{figure}[t!]
%  \begin{code}
%    \Template{S}
%      Match[100] \PREFIX=\$GP, \PEER=\{AG, AL\}
%        \PEER \Arrow *
%      Match[100] \PREFIX=\$LP, \PEER=\{AG, AL\}
%        \PEER \Arrow \{AG, AL\}
%      Match[110] \PREFIX=true \PEER=\{P1\},
%        \PEER \Arrow *, \COMM \Arrow (1,0)
%      Match[100] \PREFIX=true \PEER=\{P2\},
%        \PEER \Arrow *, \COMM \Arrow (0,1)
%      ...
%  \end{code}%

%  \vspace{-2em}
%  \begin{code}
%    \Router{S1, S2}
%      Match[100] \PREFIX=GP1, \PEER=\{AG1, AL1, ...\}
%        \PEER \Arrow *
%      Match[100] \PREFIX=GP2, \PEER=\{AG1, AL1, ...\}
%        \PEER \Arrow *
%      ...
%      Match[100] \PREFIX=LP1, \PEER=\{AG1, AL1, ...\}
%        \PEER \Arrow \{AG1, AL1, ...\}
%      Match[100] \PREFIX=LP2, \PEER=\{AG1, AL1, ...\}
%        \PEER \Arrow \{AG1, AL1, ...\}
%      ...
%      Match[110] \PREFIX=true, \PEER=\{P1\},
%        \PEER \Arrow *, \COMM \Arrow (1,0)
%      Match[100] \PREFIX=true, \PEER=\{P2\},
%        \PEER \Arrow *, \COMM \Arrow (0,1)
%      ...
%    \end{code}

  \begin{center}
  \includegraphics[width=.8\columnwidth]{figures/configs}  
  \end{center}
  \vspace{-1em}
  \caption{Spine template and concrete configurations.}
  \label{fig:bgp-configs}
\end{figure}
